\huge Tor's Usability for Censorship Circumvention

### 2016-05-09 pets2017-paper/pets2017-paper.tex
future work rewording.

\section{Future Work} 
We collaborated and communicated with Tor developers throughout the qualitative user study, redesign of the interface, and the quantitative user study. Redesigning the configuration interface was a mutual interest. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. We plan to work with Tor developers to integrate helpful changes. This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.

We took an approach that optimized for the average case user manually configuring a connection. Additional user studies that focus specifically on users in heavily censored environments or increasing the amount of automation in the configuration process may yield higher rates of success and faster time to success. We list 3 approaches that can seem worth exploring. \\

\begin{description}
\item{\bfseries Automate the configuration.} One naive way to automate the process users should take, trying the most likely configurations to work in order. This process leaks to network eavesdroppers that the user is connecting to the Tor network, but this would not harm users today (as far as we know). Our study finds that 64\% users fail on the first try when trying to circumvent an advanced censor. However, further research can explore if and how much increased risk is associated with this approach. 
\item{\bfseries Ask about the risk.} Automating the configuration process for all who are not at risk and offering manual configuration to those who would like to be more cautious is an alternative to complete automation. The complication with this approach is that we would need to ask the users whether they would be at risk if someone learned that they are connecting to the Tor network. Users may not be qualified to answer this question or may not trust Tor with this information. 
\item{\bfseries Ask if users know what to do.} Automating the process for users who do not know how to configure a bridge or proxy could be an alternative option. However, there are ethical implications of making mistakes on behalf of users at risk.
\end{description}

>>>>

\section{Future Work} 
Our goal was to deploy impactful, tested changes the Tor configuration interface. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away. For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed. However, we list some alternative approaches that seem worth exploring. \\

\begin{description}
\item{\bfseries Automate the configuration.} The most efficient way to connect as many users to the Tor network is to automatically configure their connection on start. A naive automation is to try configurations that would most likely work, in order (i.e. a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy). This leaks to network eavesdroppers that the user is connecting to the Tor network. We do not know how much risk is associated with this approach. 
\item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk. The complication with this approach is that users may not be qualified to answer if they are at risk or may not trust Tor with this information. 
\item{\bfseries Ask if users know what to do.} Another alternative to naive automation is to offer manual configuration to those that know how to configure their connection and to automate the process for users who do not know how to configure their connection. This may prevent the most mistakes, but does not account for the users' risk associated with using Tor. 
\item{\bfseries Suggest configurations.} A way to help users without any automation or questions is to give users information about what would work in their country. The first page of the configuration interface can show a list of countries with a corresponding recommended configuration. This approach does not require users to answer about their risk, technical ability, or location. However, it does require that the user trust the given advice and to correctly configure their settings based on this advice. 
\item{\bfseries Assign configurations.} This is a smart way to automate connections to the Tor network. Upon start, the interface detects proxy settings and uses them, if any. Then, all users connect to bridges that will always work (such as meek bridges), which assign them a guard relay based on their location, effectively assigning bridges for the user. 
\end{description}
